The Power of Dependent Reflection

### 2021-07-05 paper.tex
Add code for main extraction example

\usepackage{varwidth}

@@

@@

@@

% Agda Basics and Extraction
\input{latex/background}
\input{latex/psembedding}

\section{Extraction}
\subsection{Framework Overview}
Explain very briefly that there is a common extraction part that we can (and do)
abstract away; and there is a language part that we are focusing on.  This can be
moved towards the end.

\subsection{PostScript Programs Repesentation}
Explain the AST and show encoding of an example.

\subsection{\label{sec:normalisation}Normalisation}
It is useful for inlining functions, and creating macros that can use arbitrary expressions
as long as their applications evaluate to postscript operators.
This is not essential and can be moved towards the end.

%\subsubsection{Telescopes}
\subsection{\label{sec:controlling-reduction}Controlling Reduction}
This is essential, as we need to avoid inlining of the base operators, otherwsie
we won't be able to extact our pograms one-to-one.  Explain the mechanism.  Say that we have
added this to Agda?

\subsection{\label{sec:maptypes}Analysing Types}
Explain that all we need to do is to find the position of the stack argument, as well as
verify that the return type is also a stack argument.  In between we can have arbitrary
number of computationally irrelevant arguments.

\subsection{Pattern Matching}
The natural way to express functions in Agda is by means of pattern-matching, so it makes sense
to support it.  All we allow in patternmatching is to ``look'' at the stack argument and the
individual elements.  But we are not allowed to reshuffle the elements, we have to pass the
pattern exactly as it was matched (in some sense it is read-only pattern matching).

\subsection{\label{sec:translating-terms}Translating terms}
The core of the extraction is how do we translate terms.  Also this is the simplest part in
case of the PostScript example.

\subsection{Example}
Explain the entire extaction process for the given example?

Shall we talk about termination and how do we deal with that?

\subsection{\label{sec:rewriting}Rewriting}
We can mention that rewriting is super useful feature that can be used as an optimisation
prior to extraction.

>>>>

\usepackage{varwidth}
\usepackage{microtype}

@@

\usepackage[T1]{fontenc}

@@

\newunicodechar{←}{\ensuremath{\leftarrow}}
\newunicodechar{×}{\ensuremath{\times}}
\newunicodechar{λ}{\ensuremath{\lambda}}
\newunicodechar{∀}{\ensuremath{\forall}}
\newunicodechar{Π}{\ensuremath{\Pi}}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{≅}{\ensuremath{\cong}}
\newunicodechar{≐}{\ensuremath{\doteq}}
\newunicodechar{∈}{\ensuremath{\in}}
\newunicodechar{∧}{\ensuremath{\land}}
\newunicodechar{∨}{\ensuremath{\lor}}
\newunicodechar{⊤}{\ensuremath{\top}}
\newunicodechar{⊥}{\ensuremath{\bot}}
\newunicodechar{⊔}{\ensuremath{\sqcup}}
\newunicodechar{∷}{\ensuremath{{::}}}
\newunicodechar{ℓ}{\ensuremath{\ell}}
\newunicodechar{₀}{\ensuremath{{_0}}}
\newunicodechar{₁}{\ensuremath{{_1}}}
\newunicodechar{₂}{\ensuremath{{_2}}}
\newunicodechar{₃}{\ensuremath{{_3}}}
\newunicodechar{₄}{\ensuremath{{_4}}}
\newunicodechar{₅}{\ensuremath{{_5}}}
\newunicodechar{₆}{\ensuremath{{_6}}}
\newunicodechar{₇}{\ensuremath{{_7}}}
\newunicodechar{₈}{\ensuremath{{_8}}}
\newunicodechar{₉}{\ensuremath{{_9}}}
\newunicodechar{⟨}{\ensuremath{{\langle}}}
\newunicodechar{⟩}{\ensuremath{{\rangle}}}
\newunicodechar{̧}{\c}
\newunicodechar{≤}{\ensuremath{\leq}}
\newunicodechar{ℕ}{\ensuremath{\mathbb{N}}}
\newunicodechar{∸}{̣\ensuremath{-}}
\newunicodechar{ᵇ}{\ensuremath{{}^{b}}}

@@

% Agda Basics and Extraction
\input{latex/background}
\input{latex/psembedding}
\input{latex/extraction}
